Modelling BCG vaccination in the UK

### 2019-07-31 rmds/09-model-fitting.Rmd
finalised imported findings

```{r 09-scenarios-table, eval = FALSE}
tibble(Scenario = names(scenario_dics) %>% str_split("_") %>% 
         map_chr(~paste(., collapse = " ")), 
       DIC = unlist(transpose(scenario_dics)$dic)) %>% 
  arrange(DIC) %>% 
  mutate(Scenario = Scenario %>% 
           str_replace("plus", "and") %>% 
           str_replace("baseline", "Baseline") %>% 
           str_replace("transmission", "Transmission variable in young adults (15-29)") %>% 
           str_replace("mixing", "non-UK born mixing variable in young adults (15-29)") %>% 
  str_to_sentence()) %>% 
kable(
  caption = "DIC values for each scenario evaluated during model fitting - arranged from best to worst model fit.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 09-table-incidence-preds, eval = FALSE}
sum_obs_table %>% 
  set_names(., nm = c(names(.)[-ncol(.)], "Predicted Incidence (95% CI)*")) %>% 
kable(
  caption.short = "Observed versus predicted overall TB incidence for years that the model was fitted too.", 
  caption = "Observed versus predicted overall TB incidence for years that the model was fitted too. The model underpredicted incidence for all years fitted too. The upper credible interval of the model predictions was substantially lower than the observed data. ", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = "* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile.", notation = "none")
```

@@

```{r 09-fig-prior-params, fig.scap = "Prior and posterior distributions for fitted model parameters.", fig.cap = paste0("Prior and posterior distributions for fitted model parameters. Parameter names in figure are in their coded form. They can be interpreted using the following: ", legend_params)}
knitr::include_graphics(file.path(plots_path, "prior-posterior-overview-1.png"))
```

```{r 09-prior-posterior}
sum_prior_posterior %>% 
  set_names(., nm = . %>% 
              str_replace("or", "or (95%CI)\\*\\*")) %>%
kable(
  caption.short = "Observerd versus predicted overall TB incidence for years that the model was fitted too.", 
  caption = "Observerd versus predicted overall TB incidence for years that the model was fitted too. The model underpredicted incidence for all years fitted too. The upper credible interval of the model predictions was substantially lower than the observed data. ",
  booktabs = TRUE, longtable = TRUE, escape = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = c("* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile."),
                        notation = "none")
```

@@

* Plot parameter sensitivty
* Comment on parameter sensitivity in light of strength of data

## Discussion

@@

### Pipeline strengths and weaknesses

### Comparison to other methods

As dicussed earlier in this chapter, SMC-SMC was used for all model fitting. This uses an external SMC step to estimated the posterior distribution as well as an internal SMC step to estimate the marginal likelihood. In general bayesian model fitting approaches are beneficial as they allow prior information to be fully incorperated into model fitting and they produce true posterior distribution estimates rather than point estimates.[@Murray2015; @Toni2009] There are two main families of approaches, SMC and MCMC, both previously discussed in this chapter. Using SMC to estimate the posterior distribution has numerous advantages over MCMC. The first of these is that MCMC aproaches are sensitive to their initial conditions. If a model has multiple local best fits MCMC may only converge to a single minima rather than fully exploring the posterior distribution. Multiple MCMC chains may be used to try and account for this but as each chain must be independently run to convergance only a few concurrent chains are likely to be practical. SMC on the other hand is initialised with a large sample from the prior distribution, meaning that local minimas are more likely to be explored. Parameter particle weighting and resampling then balances the contribution to the posterior distribution of these local minimas based on their fit to the observed data. Additionally, MCMC approaches are by definition sequential,[@Murray2015] although if they make use of particle filters these can be run in parallel. Increasing the number of particles in a filter may lead to an increase in the chain mixing rate of the MCMC chain but as particles numbers are increased any returns will decrease. To account for this multiple chains are often used, but as outlined above the burn-in required for each chain limits the potential speed-up. In comparision, each SMC parameter particle can have it's marginal likelihood computed seperately. Although the resampling step remains a bottleneck as it can only be completed once all marginal likelihoods have been computed. On the other hand SMC is less interative than MCMC meaning that model fitting is harder to inspect when it is in progress. This is because SMC is not sequential, unlike an MCMC run for which each draw can be inspected as it is computed. Similarly, as SMC is not a sequential technique multiple runs cannot be combined. This means that model fitting must be done in a single run using a priori knowledge to judge the number of MCMC rejuvernation steps required, and the expected total run time. SMC will also have a variable run time based on the effective sample size as rejuvernation only happens when parameter particles have been depleted beyond a certain point. An additional benefit of SMC approaches are that they can theoretically be extended to model selection as well as parameter posterior estimation - effectively estimating posteriors for candidate model structures.[@Toni2009] Beyond SMC and MCMC there are multiple other model fitting algorithms that each have their own strengths and benefits - discussion of these is outside the scope of this thesis.

The particle filter has been shown to provide an unbiased estimate of the likelihood for arbitary state-space models.[@Murray2015] As a full information technique the particle filter provides a more accurate estimate of the likelihood than other approximate techniques, with relatively little tuning or user interaction.[@Murray2015] The major downside of the particle filter, compared to other approaches, is the high compute requirements, with each particle requiring a full model simulation. For highly complex models, the particle filter approach may not be tractable or a reduced level of accuracy of the marginal likelihood estimate must be accepted. In addition, the bootstrap particle filter may become depleted (i.e variance between particles is reduce to such an extent that the effective sample size becomes small) when the model being fitted is a poor fit for the observed data.[@Murray2015] Whilst this can be resolved using additional particles, or rejuvernation steps, this may not be computationally tractable. There are several alternative particle filters that seek to mitigate these issues but many of them are highly complex and do not significantly reduce the required compute - see [@Murray2015] for a detailed discussion of some of these alternatives. An alternative approach to a particle fitler is to use an approximate technique, such as approximate bayesian computation (ABC). ABC can be used to estimate the likelihood by comparing observed and simulated data.[@Toni2009] This dramatically reduces the required compute as multiple model simulations per parameter set are no longer required. The comparison between the observed and simulated data is facilitated using a distance function with parameter sets being accepted if they are within some thresold distance. This thresold can be be tuned to produce a good estimate of the posterior distribution. Developing a distance function for all of the observed data can often be challenging so instead the distance is often calculated using a set of summary features.[@Toni2009] In principle, ABC can be used with a wide variety of algorithms (including a simple rejection approach, MCMC, and SMC) to estimate the posterior distribution but in practise it has been shown that ABC-SMC generally performs better than alternative ABC approaches.[@Toni2009] The two major limitations of ABC compared to the use of a particle filter is that in most cases summary statistics must be used rather than calculating the distance from the observed data and a function for calculating the distance must also be chosen.[@Toni2009; @Lintusaari2016] Whilst some techniques exist for evaluating summary statistics the choice is often subjective, relying on domain knowledge.[@Lintusaari2016] Chosen summary statistics rarely capture the information contained in the observed data fully and can inflate posterior distribution and in the worst cases introduce bias to the estimates.[@Busetto2013]

### Comparison to other software

@@

There are many other tools available within the `R` ecosystem for fitting infectious disease models and detailing them all is beyond the scope of this thesis. However, `LibBi` and `rbi` represent an attempt to provide a complete modelling framework rather than being a simple toolbox for model fitting. The `pomp` package has a similar aim making a comparison worthwhile.[@King2016] `pomp` defines models using a similiar structure to that presented here and used within `LiBbi`. However, rather than using its own modelling language it relies on the use of either `R` or `C` code. This has several advantages in that `pomp` models can more easily be generalised, can be understood and implemented by users new to the package and can make use of packages from the wider `R` and `C` ecosystem. The downside to this approach is that for complex models the use of `C` is essentially a requirement for efficiency reasons and implementing complex models in `C` can be an error prone and time consuming process. `pomp` offers support for PMCMC, iterated filtering, and ABC-MCMC but does not support SMC based aproaches (such as SMC-SMC and ABC-SMC).[@King2016] In developing the work presented here, and in the previous chapter, a simpler model was developed using `pomp`. This work was not included in this thesis as it was not sufficiently developed. However, it highlight similar issues with the `pomp` package to those observed when using `LibBi`. Whilst `pomp`'s documentation, stability, and testing were much improved over `LibBi` it had similar limitations when it came to complex models. This was to such an extent that I developed numerous helper functions to deal with both the input and output of `pomp` models^[idmodelr: https://github.com/seabbs/idmodelr]. `pomp`'s documentation also has a heavy focus on iterated filtering over other model fitting techniques.

@@

Whilst the results presented here are not encouraging it may be the case that with a greatly extended runtime a much better fitting model may be found. The first step to testing this is to rerun the pipeline using several orders of magnitude more rejuvernation steps - as these have no RAM overhead. Even if the resulting model fits are still poor this may indicate areas for improvement - in either the model fitting pipeline or the model itself. An alternative option is to recode the model developed in the last chapter into a more generic form (i.e C) and to attempt to fit the model using other techniques that are less compute intensive and more robust - such as SMC-ABC. A final option would be to reimplement the model in the form required by another modelling package - such as `pomp`. However, this would mean running the risk of again getting stuck within a framework that is difficult to debug and may not be working as expected.

@@

* Defined the disease transmission model from the previous chapter as a state-space model. 
* Outlined the observed data and defined an appropriate measurement model for this data. 
* Developed a model fitting pipeline based on SMC-SMC to fit the previously defined state-space model to TB notification data.
* Discussed ad-hoc approaches used to improve model fit. 
* Evaluated the various scenarios discussed in the previous chapter using DIC and discussed the implications of these findings. 
* Presented the model fit to data from the best fitting scenario as established using the DIC. 
* Discussed the posterior distributions of the fitted parameters and compared these distributions to the prior distributions.
* Estimated the model sensitivity to parameter changes and discussed the impact that this sensitivity may have.

>>>>

```{r 09-scenarios-table, eval = FALSE}
tibble(Scenario = names(scenario_dics) %>% str_split("_") %>% 
         map_chr(~paste(., collapse = " ")), 
       DIC = unlist(transpose(scenario_dics)$dic)) %>% 
  arrange(DIC) %>% 
  mutate(Scenario = Scenario %>% 
           str_replace("plus", "and") %>% 
           str_replace("baseline", "Baseline") %>% 
           str_replace("transmission", "Transmission variable in young adults (15-29)") %>% 
           str_replace("mixing", "non-UK born mixing variable in young adults (15-29)") %>% 
  str_to_sentence()) %>% 
mutate(DIC = round(DIC, 0)) %>% 
kable(
  caption = "DIC values for each scenario evaluated during model fitting - arranged from best to worst model fit.", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position"))
```

@@

```{r 09-table-incidence-preds, eval = FALSE}
sum_obs_table %>% 
  set_names(., nm = c(names(.)[-ncol(.)], "Predicted Incidence (95% CI)*")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "Observed versus predicted overall TB incidence for years that the model was fitted too.", 
  caption = "Observed versus predicted overall TB incidence for years that the model was fitted too. The model underpredicted incidence for all years fitted too. The upper credible interval of the model predictions was substantially lower than the observed data. ", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = "* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile.", notation = "none")
```

@@

```{r 09-fig-prior-params, fig.scap = "Prior and posterior distributions for fitted model parameters.", fig.cap = paste0("Prior and posterior distributions for fitted model parameters. Parameter names in figure are in their coded form. They can be interpreted using the following: ", param_legend)}
knitr::include_graphics(file.path(plots_path, "prior-posterior-overview-1.png"))
```

```{r 09-prior-posterior}
sum_prior_posterior %>% 
  set_names(., nm = . %>% 
              str_replace("or", "or (95%CI)\\*\\*")) %>%
  mutate(Parameter = latex_param) %>% 
  select(-latex_param) %>% 
kable(
  caption.short = "Observerd versus predicted overall TB incidence for years that the model was fitted too.", 
  caption = "Observerd versus predicted overall TB incidence for years that the model was fitted too. The model underpredicted incidence for all years fitted too. The upper credible interval of the model predictions was substantially lower than the observed data. ",
  booktabs = TRUE, longtable = TRUE, escape = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = c("* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile."),
                        notation = "none")
```

@@

* Comment on parameter sensitivity in light of strength of data

```{r 09-fig-sens, fig.scap = "Partial rank correlation coefficients for each parameter fitted too.", fig.cap = paste0("Partial rank correlation coefficients for each parameter fitted too. Parameter names in figure are in their coded form. They can be interpreted using the following: ", param_legend)}
knitr::include_graphics(file.path(plots_path, "incidence-sensitivity-1.png"))
```
## Discussion

@@

As dicussed earlier in this chapter, SMC-SMC was used for all model fitting. This uses an external SMC step to estimated the posterior distribution as well as an internal SMC step to estimate the marginal likelihood. In general bayesian model fitting approaches are beneficial as they allow prior information to be fully incorperated into model fitting and they produce posterior distribution estimates rather than point estimates.[@Murray2015; @Toni2009] There are two main families of approaches, SMC and MCMC, both previously discussed in this chapter. Using SMC to estimate the posterior distribution has numerous advantages over MCMC. The first of these is that MCMC aproaches are sensitive to their initial conditions. If a model has multiple local best fits MCMC may only converge to a single minima rather than fully exploring the posterior distribution. Multiple MCMC chains may be used to try and account for this but as each chain must be independently run to convergance only a few concurrent chains are likely to be practical. SMC on the other hand is initialised with a large sample from the prior distribution, meaning that local minimas are more likely to be explored. Parameter particle weighting and resampling then balances the contribution to the posterior distribution of these local minimas based on their fit to the observed data. Additionally, MCMC approaches are by definition sequential,[@Murray2015] although if they make use of particle filters these can be run in parallel. Increasing the number of particles in a filter may lead to an increase in the chain mixing rate of the MCMC chain but as particles numbers are increased any returns will decrease. To account for this multiple chains are often used, but as outlined above the burn-in required for each chain limits the potential speed-up. In comparision, each SMC parameter particle can have it's marginal likelihood computed seperately. Although the resampling step remains a bottleneck as it can only be completed once all marginal likelihoods have been computed. On the other hand SMC is less interative than MCMC meaning that model fitting is harder to inspect when it is in progress. This is because SMC is not sequential, unlike an MCMC run for which each draw can be inspected as it is computed. Similarly, as SMC is not a sequential technique multiple runs cannot be combined. This means that model fitting must be done in a single run using a priori knowledge to judge the number of MCMC rejuvernation steps required, and the expected total run time. SMC will also have a variable run time based on the effective sample size as rejuvernation only happens when parameter particles have been depleted beyond a certain point. An additional benefit of SMC approaches are that they can theoretically be extended to model selection as well as parameter posterior estimation - effectively estimating posteriors for candidate model structures.[@Toni2009] Beyond SMC and MCMC there are multiple other model fitting algorithms that each have their own strengths and benefits - discussion of these is outside the scope of this thesis.

The particle filter has been shown to provide an unbiased estimate of the likelihood for arbitary state-space models.[@Murray2015] As a full information technique the particle filter provides a more accurate estimate of the likelihood than other approximate techniques, with relatively little tuning or user interaction.[@Murray2015] The major downside of the particle filter, compared to other approaches, is the high compute requirements, with each particle requiring a full model simulation. For highly complex models, the particle filter approach may not be tractable or a reduced level of accuracy of the marginal likelihood estimate must be accepted. In addition, the bootstrap particle filter may become depleted (i.e variance between particles is reduce to such an extent that the effective sample size becomes small) when the model being fitted is a poor fit for the observed data.[@Murray2015] Whilst this can be resolved using additional particles, or rejuvernation steps, this may not be computationally tractable. There are several alternative particle filters that seek to mitigate these issues but many of them are highly complex and do not significantly reduce the required compute - see [@Murray2015] for a detailed discussion of some of these alternatives. An alternative approach to the particle fitler is to use an approximate technique, such as approximate bayesian computation (ABC). ABC can be used to estimate the likelihood by comparing observed and simulated data.[@Toni2009] This dramatically reduces the required compute as multiple model simulations per parameter set are no longer required. The comparison between the observed and simulated data is facilitated using a distance function with parameter sets being accepted if they are within some thresold distance. This thresold can be be tuned to produce a good estimate of the posterior distribution. Developing a distance function for all of the observed data can often be challenging so instead the distance is often calculated using a set of summary features.[@Toni2009] In principle, ABC can be used with a wide variety of algorithms (including a simple rejection approach, MCMC, and SMC) to estimate the posterior distribution but in practise it has been shown that ABC-SMC generally performs better than alternative ABC approaches.[@Toni2009] The two major limitations of ABC compared to the use of a particle filter is that in most cases summary statistics must be used rather than calculating the distance from the observed data and a function for calculating the distance must be chosen.[@Toni2009; @Lintusaari2016] Whilst some techniques exist for evaluating summary statistics the choice is often subjective, relying on domain knowledge.[@Lintusaari2016] Chosen summary statistics rarely capture the information contained in the observed data fully and can inflate posterior distribution and in the worst cases introduce bias to the estimates.[@Busetto2013] The choice of distance function may also incluence the estimates of the posterior distribution.[@Lintusaari2016]

@@

There are many other tools available within the `R` ecosystem for fitting infectious disease models and detailing them all is beyond the scope of this thesis. However, `LibBi`, `rbi`, and `rbi.helpers` represent an attempt to provide a complete modelling framework rather than being a simple toolbox for model fitting. The `pomp` package has a similar aim making a comparison worthwhile.[@King2016] `pomp` defines models using a similiar structure to that presented here and used within `LiBbi`. However, rather than using its own modelling language it relies on the use of either `R` or `C` code. This has several advantages in that `pomp` models can more easily be generalised, can be understood and implemented by users new to the package and can make use of packages from the wider `R` and `C` ecosystem. The downside to this approach is that for complex models the use of `C` is essentially a requirement for efficiency reasons and implementing complex models in `C` can be an error prone and time consuming process. `pomp` offers support for PMCMC, iterated filtering, and ABC-MCMC but does not support SMC based aproaches (such as SMC-SMC and ABC-SMC).[@King2016] In developing the work presented here, and in the previous chapter, a simpler model was developed using `pomp`. This work was not included in this thesis as it was not sufficiently developed. However, it highlight similar issues with the `pomp` package to those observed when using `LibBi`. Whilst `pomp`'s documentation, stability, and testing were much improved over `LibBi` it had similar limitations when it came to complex models. This was to such an extent that I developed numerous helper functions to deal with both the input and output of `pomp` models^[idmodelr: https://github.com/seabbs/idmodelr]. `pomp`'s documentation also has a heavy focus on iterated filtering over other model fitting techniques.

@@

Whilst the results presented here are not encouraging it may be the case that with a greatly extended runtime a much better fitting model may be found. The first step to testing this is to rerun the pipeline using several orders of magnitude more rejuvernation steps - as these have no RAM overhead. Even if the resulting model fits are still poor this may indicate areas for improvement - in either the model fitting pipeline or the model itself. An alternative option is to recode the model developed in the last chapter into a more generic form (i.e C) and to attempt to fit the model using other techniques that are less compute intensive and more robust - such as SMC-ABC. Another option would be to reimplement the model in the form required by another modelling package - such as `pomp`. However, this would mean running the risk of again getting stuck within a framework that is difficult to debug and may not be working as expected. A final option would be to reduce the complexity of the model and potentially fit to less complex data. This may be the only solution if the current model is not identifiable.

@@

* Defined the disease transmission model from the previous chapter as a state-space model. 
* Outlined the observed data and defined an appropriate measurement model for this data. 
* Developed a model fitting pipeline based on SMC-SMC to fit the previously defined state-space model to TB notification data.
* Discussed ad-hoc approaches used to improve model fit. 
* Evaluated the various scenarios discussed in the previous chapter using DIC and discussed the implications of these findings. 
* Presented the model fit to data from the best fitting scenario as established using the DIC. 
* Discussed the posterior distributions of the fitted parameters and compared these distributions to the prior distributions.
* Estimated the model sensitivity to parameter changes and discussed the impact that this sensitivity may have.
* Discussed the strengths and limitations of the work presented here, as well as outlining potential further work.

### 2019-07-31 rmds/10-model-results.Rmd
finalised imported findings

## Comparing vaccination scenarios with observed data

  * Comparision of cases.
  * Comparision of age distribution of deaths.
  * All in reflection of reality.

```{r 10-overview-fig, fig.scap = "Observed and predicted TB incidence stratified by model age group", fig.cap = "Observed and predicted TB incidence stratified by model age group (0-11). 0-9 refers to 5 year age groups from 0-4 years old to 45-49 years old. 10 refers to those aged between 50 and 69 and 11 refers to those aged 70+. The model underpredicted incidence in all age groups fitted too with older adults have the best fit.", eval = FALSE}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-2000-obs-1.png"))
```

@@

  * Comparision of cases at multiple time horizons (10 and 25 years).
  * Comparision of age distribution of cases.
  * Comparision of deaths at multiple time horizons (10 and 25 years).
  * Comparision of age distribution of deaths

### Summary

@@

* Continuing school-age vaccination results in lower overall incidence rates compared to both neonatal vaccination, and no vaccination. 
* Neonatal vaccination resulted in low incidence in children compared to any other scenario. 
* No vaccination led to higher incidence in all age groups when compared to school-age vaccination and in children only when comapred to neonatal vaccination.
* The impact of any vaccination on cases in older adults was small.

>>>>

@@

  * Comparision of cases at multiple time horizons (10 and 25 years).

```{r 10-overall-scenarios-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-future-1.png"))
```

```{r 10-table-future-incidence, eval = FALSE}
sum_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)\\*")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "", 
  caption = "", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = "* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile.", notation = "none")
```

  * Comparision of age distribution of cases.

```{r 10-age-scenarios-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-future-age-1.png"))
```

  * Comparision of deaths at multiple time horizons (10 and 25 years).

```{r 10-scenarios-deaths-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-1.png"))
```

```{r 10-table-deaths-preds, eval = FALSE}
sum_deaths_scenario %>% filter(Year %% 5 == 0) %>% 
  set_names(., nm = names(.) %>% str_replace_all("BCG", "BCG (95% CI)\\*")) %>% 
  select(-Observation) %>% 
kable(
  caption.short = "", 
  caption = "", booktabs = TRUE, longtable = TRUE) %>% 
  kable_styling(latex_options = c("hold_position")) %>% 
  add_footnote(label = "* 95% credible interval estimated using the 2.5% quantile and the 97.5% quantile.", notation = "none")
```

  * Comparision of age distribution of deaths

```{r 10-age-scenarios-deaths-fig, fig.scap = "", fig.cap = ""}
knitr::include_graphics(file.path(plots_path, "overview-scenarios-deaths-future-age-1.png"))
```
### Summary

@@

* Continuing school-age vaccination results in lower overall incidence rates compared to both neonatal vaccination, and no vaccination. 
* Neonatal vaccination resulted in low incidence in children compared to any other scenario. 
* No vaccination led to higher incidence in all age groups when compared to school-age vaccination and in children only when comapred to neonatal vaccination.
* The impact of any vaccination on cases in older adults was small.
* These results are indicative only due to poor quality of model fit achieved in the previous chapter (Chapter \@ref(model-fitting)).
